An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
App lemma cleanup

\begin{lemma}
  \label{lem:poly-loss-poly-risk}
  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lemma:U-convex-closed}, $\U = \Gamma(\simplex)$ is finite.
  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
\end{proof}

@@

\section{Polyhedral losses have finite optimzers}\label{app:pf-polyhedral-range-gamma}
\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}
For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$
\begin{proof}
  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.

@@

\begin{lemma} \label{lemma:U-convex-closed}
  $\U$ is a finite set, and each element $U$ is a closed, convex polyhedron.
\end{lemma}
\begin{proof}
  \bo{Do we have this proof anywhere yet?}
  \raf{The proof is in the prev section, but I think you cut the statement (was in sec 4).  I'd like it standalone, since I use it in other things, so could you put the statement back?}
  Let $p$ be in the interior of the simplex.
  For any such $p$, the polyhedral expected loss $L(\cdot;p)$ projects down to the same fixed power diagram over $\reals^d$.
  The minimizer of a polyhedral loss is always the projection of some face of the polyhedron, \bo{cite} so there are a finite number of possible minimizers and each is a closed, convex polyhedron (being a member of the power diagram or an intersection of members).
  Now for $p$ not in the interior, consider each of finitely many subsets of the outcome space and restrict $p$ to have support on this subset; repeat the above arguments.
  The total number of report sets $U$ is still finite, each a closed, convex polyhedron.
\end{proof}

>>>>

\begin{lemma}
  \label{lem:poly-loss-poly-risk}
  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
\end{proof}

@@

\section{Polyhedral losses have finite optimzers}\label{app:pf-polyhedral-range-gamma}
\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}
\begin{proof}
  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
  Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.

@@
